---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ZEUS

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

ZEUS is an R package for importing Axon Binary Format (`.abf`) electrophysiology
recordings, applying ZEUS C0 and C1 stimulus-response protocol metadata, and
producing validation-ready waveform summaries, plots, and exports for ERG
analysis.

## What ZEUS includes

- Import helpers for raw ABF recordings
- Stimulus-response labeling for ZEUS C0 and C1 protocols
- Averaging, baseline correction, and smoothing utilities
- Peak-summary tables and validation helpers
- Plotting functions for mean, spectral, and intensity-response waveforms
- A Shiny app for interactive review and export

## Installation

You can install the development version of ZEUS from GitHub with:

``` r
# install.packages("pak")
pak::pak("lo2252/zeus")
```

## Example

The package includes example ABF files in `inst/extdata`. A typical workflow is:

```{r example, eval = FALSE}
library(ZEUS)

abf_path <- system.file("extdata", "26225004.abf", package = "ZEUS")

x <- zeus_read_abf(
  path = abf_path,
  protocol = "C1"
)

head(x$traces_70)

zeus_plot_mean_waveform(x)

zeus_summarize_peak_statistics(x)$key_statistics
```

To launch the interactive Shiny workflow:

```{r shiny-app, eval = FALSE}
run_zeus_app()
```
